Upgrades to the SINQ Cold Neutron Source

### 2015-09-09 paper.tex
more results

Need to investigate REH sensitivity to vertical changes
Smaller study to determine exact dimensions
Extend D2 volume instead of Pb-208 reflector
H2 cold spots
Affect on non-REH side
Make switch in MCNP reflectivity patch to reduce weight instead of leaking unreflected neutrons

>>>>

This study has only determined the horizontla geometry of the re-entrant hole in the cold source at SINQ.  Another study is needed to investigate REH sensitivity to vertical changes, as well as a parametric study over a smaller range near the optimal point to determine more exact dimensions.  The affect the REH has on the neutron flux on the opposite side will also be determined.

Different types of reflector materials and configurations will also be investigated.  The refector sits behind the cold source on the side opposite the target and reducing cold neutron losses in it may increase the guide exit current.  Adding a belt of liquid H$_2$ to produce a ``cold spot'' for focusing instruments will also be investigated.  In these studies, the flux reconstruction method will once again be used.

Futher development of the guide refelctivity patch for MCNP 6.1 will also be done.  Specifically, making a switch to reduce neutron weight upon reflection instead of leaking non-reflected neutrons in order to speed up in-beam calculations where this signal is of interest and not the noise.
